Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks.

### 2020-06-09 main.Rmd
Added acc and f1_score table, conf_mat plot of DeepT3 data classification result to main.Rmd

@@

>>>>

```{r accf1scoredeept3data}
apa_table(
  readr::read_csv("data/processed/acc_f1score_result_deept3_data_prediction.csv"),
  digits = 4,
  align = 'c',
  caption = 'Accuracy and F1-Score from prediction results of three different DeepT3 positive datasets evaluated on our model and DeepT3.',
  placement = "H"
)
```

@@

```{r deept3datacfmat, fig.height=8, fig.cap="Confusion matrices of classifications made by our bacteria model compared with DeepT3 evaluated on positive EffectiveT3 data.", fig.pos="H", message=FALSE}

readr::read_csv("data/processed/conf_mat_deept3_data_prediction.csv") %>% 
  dplyr::mutate(
  tool = factor(tool, levels = c("ensemble_weighted", "deept3"))
  ) %>% 
  ggplot2::ggplot() +
  ggplot2::aes(x = Truth, y = Prediction) +
  ggplot2::geom_tile(ggplot2::aes(fill = Freq), colour = "white") +
  ggplot2::geom_text(ggplot2::aes(label = Freq), vjust = 0.5) +
  ggplot2::facet_grid(data ~ tool) +
  ggplot2::scale_fill_viridis_c(begin = 0.2, end = 1) +
  ggplot2::labs(x = "True value", y = "Prediction") +
  ggplot2::coord_fixed()
```
